Accurate binding of sodium and calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-12-18 Manuscript/manuscript.tex
New smooth isocontours figure with according changes in MS.

\begin{figure}[tb!]
  \centering
  \includegraphics[width=8.0cm]{../Fig/isocontours_r37_ca_O-carb.png} %\\
%  \includegraphics[width=4.0cm]{../Fig/volmap_resid10_Ca_Cl_sn1Cent.png}
%  \includegraphics[width=3.6cm]{../Fig/volmap_resid10_Ca_Cl_sn2Cent.png}
  \caption{\label{fig:volmaps}
    Isocontours of spatial number density of \ce{Ca^{2+}} (dark blue, 0.0016~\AA$^{-3}$) 
    and POPC carbonyl oxygen atoms (light semi-transparent red, 0.007~\AA$^{-3}$, all POPC lipids contribute). 
    Calcium cations localize mostly around phosphate oxygens (red and bronze).
    Interactions with carbonyl oxygens is less likely than with phosphate oxygens, 
    and it is contributed more by other neighbouring phospholipids than by the same lipid. 
    Transparent structures are shown to depict the variability of choline configurations 
    (colour warps from red to blue along the simulation time). 
    The number density was evaluated for each lipid, 
    after its strucutral alignment using only phosphate group.
    MDAnalysis \cite{mdanalysis2011} library was used for 
    the calculations of the structural alignment and the spatial number density. 
    VMD \cite{hump96} was used for visualisation. 
    Carbon atoms are cyan, hydrogen atoms white, oxygen atoms red, nitrogen blue.
  }
 %\todo{The figure should be updated as discussed last week. Joe: Will only smoothen the isosurfaces now. }
\end{figure}

@@

\begin{figure}[tb!]
  \centering
  \includegraphics[width=8.2cm]{../Fig/ipython_nb/Order-parameters_form-factors_exp-L14-ECCL17_q80_sig89_POPC-struct.pdf}
  %\includegraphics[width=7.4cm]{../Fig/POPCstructure.eps}
  %\includegraphics[width=8.0cm]{../Fig/ipython_nb/Order-parameters_exp-L14-ECCL17_q80_sig89.pdf}
  %\includegraphics[height=8.4cm,angle=-90]{../Fig/form-f_exp-l14-eccl17.eps}
  \caption{\label{simVSexpNOions}
    Top: X-ray scattering form factors from simulations with the Lipid14 \cite{dickson14} and
    the ECC-POPC models compared with experiments~\cite{kucerka11} at 303~K. \\
    Middle: Order parameters of POPC head group, glycerol backbone and acyl chains 
    from simulations with the Lipid14 \cite{dickson14} and the ECC-POPC models
    compared with experiments \cite{ferreira13} at 300~K.
    The size of the markers for the head group order parameters correspond to
    the error estimate $\pm 0.02$ for experiments \cite{botan15,ollila16},
    while the error estimate for simulations is $\pm 0.005$.
    The size of the points for acyl chains are decreased by a factor of 3 to improve the clarity of the plot.
    Open/closed symbols are used for palmitoyl/oleoyl chains of POPC. \\
    Bottom: Chemical structure of POPC and the labeling of hydrocarbon segments.
  } 
\end{figure}

@@

\begin{figure}[tb!]
  \centering
  \includegraphics[width=8.0cm]{../Fig/ipython_nb/PN_angle_OrdPars-A-B_L14-ECCL17_q80_sig89_surf.pdf}
  \caption{\label{OrderParameterCHANGESsurf}
    The changes of headgroup order parameters and P-N vector orientation as a function of
    a molar fraction of the cationic surfactant dihexadecyldimethylammonium in a POPC bilayer
    from simulations and experiments \cite{scherer89} at 313 K.
  }
  \todo{Joe: currenct figure depicts simulations with OPC3 water. Simulations with SPCE are running now.}
\end{figure}

>>>>

\begin{figure}[tb!]
  \centering
  \includegraphics[width=8.0cm]{../Fig/isocontours_r37_ca_O-carb.png} %\\
%  \includegraphics[width=4.0cm]{../Fig/volmap_resid10_Ca_Cl_sn1Cent.png}
%  \includegraphics[width=3.6cm]{../Fig/volmap_resid10_Ca_Cl_sn2Cent.png}
  \caption{\label{fig:volmaps}
    Isocontours of spatial number density of \ce{Ca^{2+}} (dark blue, 0.001~\AA$^{-3}$) 
    and POPC carbonyl oxygen atoms (light semi-transparent red, 0.008~\AA$^{-3}$, all POPC lipids contribute). 
    Calcium cations localize mostly around phosphate oxygens (red and bronze).
    Interactions with carbonyl oxygens is less likely than with phosphate oxygens, 
    and it is contributed more by other neighbouring phospholipids than by the same lipid. 
    Transparent structures are shown to depict the variability of choline configurations 
    (colour warps from red to blue along the simulation time). 
    The number density was evaluated for each lipid, 
    after its strucutral alignment using only phosphate group.
    MDAnalysis \cite{mdanalysis2011} library was used for 
    the calculations of the structural alignment and the spatial number density. 
    VMD \cite{hump96} was used for visualisation. 
    Carbon atoms are cyan, hydrogen atoms white, oxygen atoms red, nitrogen blue.
  }
 %\todo{The figure should be updated as discussed last week. Joe: Will only smoothen the isosurfaces now. }
\end{figure}

@@

\begin{figure}[tb!]
  \centering
  \includegraphics[width=8.2cm]{../Fig/ipython_nb/Order-parameters_form-factors_exp-L14-ECCL17_q80_sig89_POPC-struct.pdf}
  %\includegraphics[width=7.4cm]{../Fig/POPCstructure.eps}
  %\includegraphics[width=8.0cm]{../Fig/ipython_nb/Order-parameters_exp-L14-ECCL17_q80_sig89.pdf}
  %\includegraphics[height=8.4cm,angle=-90]{../Fig/form-f_exp-l14-eccl17.eps}
  \caption{\label{simVSexpNOions}
    Top: X-ray scattering form factors from simulations with the Lipid14 \cite{dickson14} and
    the ECC-POPC models compared with experiments~\cite{kucerka11} at 303~K. \\
    Middle: Order parameters of POPC head group, glycerol backbone and acyl chains 
    from simulations with the Lipid14 \cite{dickson14} and the ECC-POPC models
    compared with experiments \cite{ferreira13} at 300~K.
    The size of the markers for the head group order parameters correspond to
    the error estimate $\pm 0.02$ for experiments \cite{botan15,ollila16},
    while the error estimate for simulations is $\pm 0.005$ 
    (Bayesian estimate of 95\% confidence interval \cite{scipy}).
    The size of the points for acyl chains are decreased by a factor of 3 to improve the clarity of the plot.
    Open/closed symbols are used for palmitoyl/oleoyl chains of POPC. \\
    Bottom: Chemical structure of POPC and the labeling of hydrocarbon segments.
  } 
\end{figure}

@@

\begin{figure}[tb!]
  \centering
  \includegraphics[width=8.0cm]{../Fig/ipython_nb/PN_angle_OrdPars-A-B_L14-ECCL17_q80_sig89_surf.pdf}
  \caption{\label{OrderParameterCHANGESsurf}
    The changes of headgroup order parameters and P-N vector orientation as a function of
    a molar fraction of the cationic surfactant dihexadecyldimethylammonium in a POPC bilayer
    from simulations and experiments \cite{scherer89} at 313 K.
  }
\end{figure}
